---
title: 'R Code'
output:
  html_notebook: default
  pdf_document: default
---

```{r Libraries Import}
library(plyr)
library(tidyverse)
library(Synth)
library(SCtools)
library(data.table)
library(bit64)
library(zoo)
library(readxl)
```

# Data Preparation

We start by creating BC's dataset.
```{r BC data preparation}
#We import all of the datasets that will be needed to compute BC's dependent variable and predictors

dataBCCO2 <-
  fread("/Users/enrico/Documents/Universita/Bocconi Bachelor/Tesi/ActualData/StatCanBCCO2.csv")

dataBCGDP <-
  fread("/Users/enrico/Documents/Universita/Bocconi Bachelor/Tesi/ActualData/StatCanBCGDP.csv")

dataBCGDPPre1997 <-
  fread(
    "/Users/enrico/Documents/Universita/Bocconi Bachelor/Tesi/ActualData/StatCanBCGDPPre.csv"
  )

dataBCGDP2018 <-
  fread(
    "/Users/enrico/Documents/Universita/Bocconi Bachelor/Tesi/ActualData/StatCanBCGDP2018.csv"
  )

dataBCCPI <-
  fread("/Users/enrico/Documents/Universita/Bocconi Bachelor/Tesi/ActualData/StatCanBCCPI.csv")

dataBCPopulation <-
  fread(
    "/Users/enrico/Documents/Universita/Bocconi Bachelor/Tesi/ActualData/StatCanBCPopulation.csv"
  )

dataBCEnergyProduction <-
  fread(
    "/Users/enrico/Documents/Universita/Bocconi Bachelor/Tesi/ActualData/StatCanBCEnergyProduction.csv"
  )

dataBCEnergyProductionPre <-
  fread(
    "/Users/enrico/Documents/Universita/Bocconi Bachelor/Tesi/ActualData/StatCanBCEnergyProductionPre.csv"
  )

year_quarter <-
  c(
    "1991-01",
    "1992-01",
    "1993-01",
    "1994-01",
    "1995-01",
    "1996-01",
    "1997-01",
    "1998-01",
    "1999-01",
    "2000-01" ,
    "2001-01",
    "2002-01",
    "2003-01",
    "2004-01",
    "2005-01",
    "2006-01",
    "2007-01",
    "2008-01",
    "2009-01",
    "2010-01",
    "2011-01",
    "2012-01",
    "2013-01",
    "2014-01",
    "2015-01",
    "2016-01",
    "2017-01",
    "2018-01",
    "2019-01"
  )

#We filter the population dataset so that it only includes annual values (note the population of each year is the one reported in the January of the next year)
dataBCPopulation <-
  dataBCPopulation[dataBCPopulation$REF_DATE %in% year_quarter]

dataBCCO2$CO2eq <- as.numeric(dataBCCO2$CO2eq)

factor <-
  dataBCCPI$VALUE[dataBCCPI$REF_DATE == "2018"] / dataBCCPI$VALUE[dataBCCPI$REF_DATE ==
                                                                    "2012"]

#Since the BC's 2018 GDP is only available in 2012 dollars we convert it to 2018 ones (using the CPI)
dataBCGDP2018$VALUE <- dataBCGDP2018$VALUE * factor

#We now add it to the table containing BC's GDP values in current dollar
dataBCGDP$VALUE[dataBCGDP$REF_DATE == "2018"] <- dataBCGDP2018$VALUE

#We add to that table the pre-1997 values as those are in a different StatCan dataset
dataBCGDP <- rbind(dataBCGDPPre1997, dataBCGDP)

#We sort this complete BC's GDP table
dataBCGDP <- arrange(dataBCGDP, REF_DATE)

years <-
  c(
    "1990",
    "1991",
    "1992",
    "1993",
    "1994",
    "1995",
    "1996",
    "1997",
    "1998",
    "1999",
    "2000",
    "2001",
    "2002",
    "2003",
    "2004",
    "2005",
    "2006",
    "2007",
    "2008",
    "2009",
    "2010",
    "2011",
    "2012",
    "2013",
    "2014",
    "2015",
    "2016",
    "2017",
    "2018"
  )

#We convert the GDP values from current dollars to 2015 constant ones using the CPI
for (i in 1:29) {
 BCCPItemp <-
  dataBCCPI$VALUE[dataBCCPI$REF_DATE == "2015"] / dataBCCPI$VALUE[dataBCCPI$REF_DATE ==
                                                                      years[i]]
  dataBCGDP$VALUE[dataBCGDP$REF_DATE == years[i]] <-
   dataBCGDP$VALUE[dataBCGDP$REF_DATE == years[i]] * BCCPItemp
}

#We convert this result in 2015 USD
dataBCGDP$VALUE <-
 dataBCGDP$VALUE * (0.7819915613) 

#We harmonize the categories identifier
dataBCGDP$COORDINATE[dataBCGDP$COORDINATE == "10.1.17"] <- "10.1.47"

dataBCGDP$COORDINATE[dataBCGDP$COORDINATE == "10.1.27"] <- "10.1.58"

#We compute BC's manufacturing carbon intensity
BCCarbonIntensity <-
  ((dataBCCO2$CO2eq[dataBCCO2$Category == "Manufacturing Industries" &
                      dataBCCO2$Region == "British Columbia" &
                      dataBCCO2$Year > 1989 &
                      dataBCCO2$Year < 2019] + dataBCCO2$CO2eq[dataBCCO2$Category == "Construction" &
                                                                 dataBCCO2$Region == "British Columbia" &
                                                                 dataBCCO2$Year > 1989 &
                                                                 dataBCCO2$Year < 2019])) /
  ((dataBCGDP$VALUE[dataBCGDP$COORDINATE ==
                                                                                                                "10.1.58"] + dataBCGDP$VALUE[dataBCGDP$COORDINATE == "10.1.47"]))



#We compute manufacturing GDP per capita
BCSectorGDPPerCapita <-
  ((dataBCGDP$VALUE[dataBCGDP$COORDINATE == "10.1.58"] + dataBCGDP$VALUE[dataBCGDP$COORDINATE ==
                                                                           "10.1.47"])*1000) / dataBCPopulation$VALUE

#We compute the share of manufacturing GDP
BCShareOfSectorGDP <-
  (dataBCGDP$VALUE[dataBCGDP$COORDINATE == "10.1.58"] + dataBCGDP$VALUE[dataBCGDP$COORDINATE ==
                                                                          "10.1.47"]) * 100 / dataBCGDP$VALUE[dataBCGDP$COORDINATE == "10.1.1"]

#We merge the two datasets containing the BC's energy demand broken up in sources
dataBCEnergyProductionPre$REF_DATE <-
  substr(dataBCEnergyProductionPre$REF_DATE,
         start = 1,
         stop = 4)

dataBCEnergyProduction <- rbind(dataBCEnergyProductionPre, dataBCEnergyProduction)

#We fill in NAs with 0s

dataBCEnergyProduction$VALUE <- na.fill(dataBCEnergyProduction$VALUE, 0)

#We compute the percentage of energy produced from low carbon sources

BCShareOfLowCarbonEnergy <- rep(0, times = 29)
for (i in 1:29) {
  BCShareOfLowCarbonEnergy[i] <-
    (sum(dataBCEnergyProduction$VALUE[dataBCEnergyProduction$`Fuel type` == "Primary electricity, hydro and nuclear" &
                                 dataBCEnergyProduction$REF_DATE == 1989 + i])) * 100 / sum(dataBCEnergyProduction$VALUE[dataBCEnergyProduction$REF_DATE ==
                                                                                                                                                                             1989 + i])
}

#We compute the expenditure on R&D as a percentage of BC's GDP (note this is available from 1997 onward)

BCShareOfResearchOverGDP <-
  (dataBCGDP$VALUE[dataBCGDP$COORDINATE == "10.1.242"]) * 100 / dataBCGDP$VALUE[dataBCGDP$COORDINATE ==
                                                                                  "10.1.1" & dataBCGDP$REF_DATE > 1996]

BCShareOfResearchOverGDP <- append(rep(NA, times = 7), BCShareOfResearchOverGDP)

#We finally create the BC's dataframe containing all of the previously computed metrics for the province

BC <-
  data.frame(
    rep("British Columbia", times = 29),
    rep(1, times = 29),
    c(1990:2018),
    BCCarbonIntensity,
    BCSectorGDPPerCapita,
    BCShareOfSectorGDP,
    BCShareOfLowCarbonEnergy,
    BCShareOfResearchOverGDP
  )

dimnames(BC)[[2]] <-
  c(
    "Country",
    "CountryNum",
    "Year",
    "CarbonIntensity",
    "SectorGDPPerCapita",
    "ShareOfSectorGDP",
    "ShareOfLowCarbonEnergy",
    "ShareOfResearchOverGDP"
  )
```

We continue by building the rest of the world dataset.
```{r ROW data preparation}
#We import all of the datasets we will use to compute the dependent variable and the predictors for the rest of the world

dataROWCO2 <-
  fread(
    "/Users/enrico/Documents/Universita/Bocconi Bachelor/Tesi/ActualData/ClimateWatchROWCO2.csv",
    header = TRUE
  )

dataROWCO2 <- as.matrix(dataROWCO2)

dataROWGDP <-
  read_excel(
    "/Users/enrico/Documents/Universita/Bocconi Bachelor/Tesi/ActualData/EuromonitorROWGDP.xlsx",
    range = "A6:AI689"
  )

dataROWPopulation <-
  read_excel(
    "/Users/enrico/Documents/Universita/Bocconi Bachelor/Tesi/ActualData/EuromonitorROWPopulation.xlsx",
    range = "A6:AH216"
  )

dataROWPopulation <- as.matrix(dataROWPopulation)

dataROWEnergyMix <-
  fread(
    "/Users/enrico/Documents/Universita/Bocconi Bachelor/Tesi/ActualData/OWIDEnergyMix.csv"
  )

dataUSCPI <-
  fread("/Users/enrico/Documents/Universita/Bocconi Bachelor/Tesi/ActualData/OECDUSCPI.csv")

dataUSCPI$Value <- as.numeric(dataUSCPI$Value)

#This is the set of countries we will use to create our Synthetic BC


countriesEuro <-
  c(
    "Japan",
    "Mexico",
    "New Zealand",
    "South Africa",
    "Turkey",
    "USA",
    "Algeria",
    "Saudi Arabia",
    "Brazil",
    "Egypt",
    "Iran",
    "Philippines",
    "Indonesia"
    )

countries <-
  c(
    "Japan",
    "Mexico",
    "New Zealand",
    "South Africa",
    "Turkey",
    "United States",
    "Algeria",
    "Saudi Arabia",
    "Brazil",
    "Egypt",
    "Iran",
    "Philippines",
    "Indonesia"
    )

#We filter the Energy Mix dataset to only include the years relevant to our analysis

dataROWEnergyMix <-
  dataROWEnergyMix[dataROWEnergyMix$Year > 1989 &
                     dataROWEnergyMix$Year < 2019]

#We create the Rest Of the World dataframe

ROW <- matrix(nrow = 0, ncol = 8)
for (c in 1:length(countries)) {
  for (i in 1:29) {
    
    #We put the country in the first column
    ROWtemp = countries[c]
    
    #We put the country's numeric identifier in the second column (the +1 is because BC is assigned to 1)
    ROWtemp = append(ROWtemp, c + 1)
                     
    #We put the year in the third column
    ROWtemp = append(ROWtemp, 1989 + i)
    
    #We take the GDP of the year and country in question
    GDPtemp = dataROWGDP[dataROWGDP$Geography == countriesEuro[c], 6 + i]
    
    GDPtemp = as.matrix(GDPtemp)
    
    GDPtemp = as.numeric(GDPtemp)
    
    #We convert this GDP in 2015 dollar value using the US CPI
    GDPtemp[2:4] = GDPtemp[2:4] * dataUSCPI$Value[dataUSCPI$TIME == "2015"] /
      dataUSCPI$Value[dataUSCPI$TIME == 1989 + i]
    
    #We take the Population of the country at the year in question
    POPtemp <-
      as.numeric(dataROWPopulation[dataROWPopulation[, 1] == countriesEuro[c], 5 +
                                     i])
    #We put the carbon intensity in the 4th column
    ROWtemp = append(ROWtemp,
                     as.numeric(dataROWCO2[dataROWCO2[, 1] == countries[c]][35 - i]) * 1000 /(GDPtemp[3] + GDPtemp[4]))
                       
    #We put the manufacturing GDP over the population in the 5th column
    ROWtemp = append(ROWtemp, ifelse(is.null(as.numeric((GDPtemp[3] + GDPtemp[4]) /
                                                          (POPtemp)
    )), NA, as.numeric((
      GDPtemp[3] + GDPtemp[4]
    ) / (POPtemp))))
    
    #We put the share of manufacturing GDP over the total in the 6th column
    ROWtemp = append(ROWtemp, as.numeric((GDPtemp[3] + GDPtemp[4]) * 100 /
                                           (as.numeric(GDPtemp[2]))))
    
    #We put the share of energy produced from low carbon sources in the 7th column
    ROWtemp = append(ROWtemp, ifelse(
      is.null(
        as.numeric(dataROWEnergyMix$`Low-carbon energy (% sub energy)`[dataROWEnergyMix$Entity ==
                                                                     countries[c] &
                                                                     dataROWEnergyMix$Year == 1989 + i])
      ),
      NA,
      as.numeric(dataROWEnergyMix$`Low-carbon energy (% sub energy)`[dataROWEnergyMix$Entity ==
                                                                   countries[c] & dataROWEnergyMix$Year == 1989 + i])
    ))
    
    #We put the Expenditure on R&D as % of GDP in the 8th column
    ROWtemp = append(ROWtemp, ifelse(is.null(GDPtemp[1]), NA, GDPtemp[1]))
    
    ROW<-rbind(ROW,ROWtemp)
}}

ROW = as.data.frame(ROW)

dimnames(ROW)[[2]] <-
  c(
    "Country",
    "CountryNum",
    "Year",
    "CarbonIntensity",
    "SectorGDPPerCapita",
    "ShareOfSectorGDP",
    "ShareOfLowCarbonEnergy",
    "ShareOfResearchOverGDP"
  )
```

We now combine the two datasets into the one we will use in our analysis.
```{r Full dataset preparation}
#We combine the BC and the Rest Of the World datasets to form the final one
Data <- rbind(ROW, BC)

#We convert all the numbers in it in doubles
Data[, 2:8] <-
  lapply(Data[, 2:8], function(x)
    if (is.character(x))
      as.numeric(x)
    else
      x)

#We put BC first
Data<-arrange(Data, CountryNum)
```

# Data Exploration

We take a look at the data.
```{r Data exploration}
#We plot our predictors and the dependent variable for all the regions in the sample
ggplot(data = Data) + geom_line(aes(x = Year, y = CarbonIntensity, color =
                                      Country))

ggplot(data = Data) + geom_line(aes(x = Year, y = SectorGDPPerCapita, color =
                                      Country))

ggplot(data = Data) + geom_line(aes(x = Year, y = ShareOfSectorGDP, color =
                                      Country))

ggplot(data = Data) + geom_line(aes(x = Year, y = ShareOfLowCarbonEnergy, color =
                                      Country))

ggplot(data = Data) + geom_line(aes(x = Year, y = ShareOfResearchOverGDP, color =
                                      Country))+xlim(1997,2018)
```
We plot the BC manufacturing emissions' path against the one for manufacturing GDP

```{r BC manufacturing GDP vs emissions}
#We collect the emissions data
BCSectorEmissions <-
  as.data.frame(((dataBCCO2$CO2eq[dataBCCO2$Category == "Manufacturing Industries" &
                                    dataBCCO2$Region == "British Columbia" &
                                    dataBCCO2$Year > 1989 &
                                    dataBCCO2$Year < 2019] + dataBCCO2$CO2eq[dataBCCO2$Category == "Construction" &
                                                                               dataBCCO2$Region == "British Columbia" &
                                                                               dataBCCO2$Year > 1989 &
                                                                               dataBCCO2$Year < 2019])))
#We collect the GDP Data
BCSectorGDP <- as.data.frame(((dataBCGDP$VALUE[dataBCGDP$COORDINATE ==
                                                 "10.1.58"] + dataBCGDP$VALUE[dataBCGDP$COORDINATE == "10.1.47"])))

#We put them together together with the years to which they refer to
DataBCEmissionsVSGDP <-
  cbind(1990:2018, BCSectorEmissions, BCSectorGDP)

#Rename the columns of the new dataframe
dimnames(DataBCEmissionsVSGDP)[[2]] <-
  c("Year", "SectorEmissions", "SectorGDP")

#Create some variables that will be useful for the plot
ylim.prim <- c(3500, 8000)

ylim.sec <- c(15000, 30000)

b <- diff(ylim.prim) / diff(ylim.sec)

a <- ylim.prim[1] - b * ylim.sec[1]

#We make the actual plot
ggplot(DataBCEmissionsVSGDP, aes(x = Year, y = SectorEmissions)) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  geom_line() +
  geom_line(aes(y = a + SectorGDP * b), color = "red") +
  scale_y_continuous("CO2e kt", sec.axis = sec_axis( ~ (. - a) / b, name = "Millions 2015 USD"))

#We save it for Latex's use
#ggsave(
#  "BCEmissionsVSGDP.png",
# width = 20,
#  height = 10,
#  units = "cm"
#)
```


# Creating the Synthetic Control Unit

We now create the synthetic control unit.
```{r Synth}
#We prepare the data
SynthData <-
  dataprep(
    foo = Data,
    predictors = c(
      "SectorGDPPerCapita",
      "ShareOfSectorGDP",
      "ShareOfLowCarbonEnergy"
    ),
    dependent = "CarbonIntensity",
    unit.variable = "CountryNum",
    unit.names.variable = "Country",
    time.variable = "Year",
    treatment.identifier = 1,
    controls.identifier = c(2:14),
    time.predictors.prior = c(1990:2007),
    time.optimize.ssr = c(1990:2007),
    time.plot = c(1990:2018),
    special.predictors = list(
      list(8, 1997:2007, "mean"),
      list(4, 1995 , "mean"),
      list(4, 2001  , "mean"),
      list(4, 2003  , "mean")
    )
  )

#We run the Synth process
Results<-synth(SynthData)

#We print its results
print(synth.tab(dataprep.res = SynthData, synth.res = Results))

#We plot its results
path.plot(
  synth.res = Results,
  dataprep.res = SynthData,
  Ylab = "CO2e kt per millions of 2015 USD",
  tr.intake = 2007
)



gaps.plot(synth.res = Results,
          dataprep.res = SynthData,
          Ylab = "CO2e kt per millions of 2015 USD of difference",
          tr.intake=2007)

```

We repeat the process setting 2005 as the end of the pre-intervention period.
```{r Synth with 2005 end}
#We prepare the data
SynthData2 <-
  dataprep(
    foo = Data,
    predictors = c(
      "SectorGDPPerCapita",
      "ShareOfSectorGDP",
      "ShareOfLowCarbonEnergy"
    ),
    dependent = "CarbonIntensity",
    unit.variable = "CountryNum",
    unit.names.variable = "Country",
    time.variable = "Year",
    treatment.identifier = 1,
    controls.identifier = c(2:14),
    time.predictors.prior = c(1990:2005),
    time.optimize.ssr = c(1990:2005),
    time.plot = c(1990:2018),
    special.predictors = list(
      list(8, 1997:2005, "mean"),
      list(4, 1995 , "mean"),
      list(4, 2001  , "mean"),
      list(4, 2003  , "mean")
      ))

#We run the Synth process
Results2 <- synth(SynthData2)

#We print its results
print(synth.tab(dataprep.res = SynthData2, synth.res = Results2))

#We plot its results
path.plot(
  synth.res = Results2,
  dataprep.res = SynthData2,
  Ylab = "CO2e kt per millions of USD",
  tr.intake = 2005
)


gaps.plot(synth.res = Results2,
          dataprep.res = SynthData2,
          Ylab = "CO2e kt per millions of 2015 USD of difference",
          tr.intake = 2005)

```

## Placebo Tests

We now run the placebo tests.
We start with the location one.
```{r location placebo}
#We run the location placebo
ResultsLocation <- generate_placebos(SynthData2, Results2)
```


```{r location placebo results}
#We plot their result without discarding any region regardless of how big the pre-intervention MSPE is
plot_placebos(ResultsLocation, discard.extreme = FALSE, ylab="CO2e kt per millions of 2015 USD of difference", xlab="Time")

#We plot their result discarding regions for which the pre-intervention MSPE is 10 times larger than BC's one
plot_placebos(ResultsLocation,
              discard.extreme = TRUE,
              mspe.limit = 10, ylab="CO2e kt per millions of 2015 USD of difference", xlab="Time")

#We plot a comparison of the different countries' pre/post-intervention MSPE ratios
mspe.plot(ResultsLocation)

#We look at the test's result
mspe.test(ResultsLocation)
```

We continue with the loo one.
```{r loo placebo}
ResultsPlaceboLOO <- matrix(nrow = 0, ncol = 4)

for (i in 1:14) {
  #eliminate one country from the vector of controls (if i==14 no country is eliminated as in the previous case)
  if (i == 14) {
    controlstemp <- countries
  }
  
  controlstemp <- countries[-i]
  
  #We prepare the data
  SynthDataLOO <-
    dataprep(
      foo = Data,
      predictors = c(
        "SectorGDPPerCapita",
        "ShareOfSectorGDP",
        "ShareOfLowCarbonEnergy"
      ),
      dependent = "CarbonIntensity",
      unit.variable = "CountryNum",
      unit.names.variable = "Country",
      time.variable = "Year",
      treatment.identifier = 1,
      controls.identifier = controlstemp,
      time.predictors.prior = c(1990:2005),
      time.optimize.ssr = c(1990:2005),
      time.plot = c(1990:2018),
      special.predictors = list(
        list(8, 1997:2005, "mean"),
        list(4, 1995, "mean"),
        list(4, 2001, "mean"),
        list(4, 2003, "mean")
      )
    )
  
  #We run the Synth process
  ResultsLOO <- synth(SynthDataLOO)
  
  #We take out the set of weights from it
  w <- ResultsLOO$solution.w
  
  #We prepare some variables for the next process
  temp <- rep(0, times = 29)
  
  temp2 <- rep(0, times = 29)
  
  t = 0
  
  #We compute the difference between the synthetic and the BC carbon intensity
  for (j in 1:13) {
    if (j == i) {
      next
      
    }
    
    t = t + 1
    
    temp <-
      temp + w[t] * Data$CarbonIntensity[Data$CountryNum == j + 1] #rename temp
  }
  
  #We create a matrix that contains the difference computed above year by year and with an indication of which country was removed when it was computed
  for (j in 1:29) {
    #We put the year as the first column
    tempres <- 1989 + j
    
    #We put the removed country as the second column
    tempres <- append(tempres, ifelse(i == 14, "No Country", countries[i]))
    
    #We put the difference between the BC and the synthetic BC carbon intensities as the third column
    tempres <-
      append(tempres, Data$CarbonIntensity[Data$Country == "British Columbia" &
                                            Data$Year == 1989 + j] - temp[j])
    
    #we put the synthetic carbon intensity as the fourth column
    tempres<-append(tempres, temp[j])
    ResultsPlaceboLOO <- rbind(ResultsPlaceboLOO, tempres)
  }
}

#We turn this into a dataframe
ResultsPlaceboLOO <- as.data.frame(ResultsPlaceboLOO)

#We rename its columns
dimnames(ResultsPlaceboLOO)[[2]] <-
  c("Year",
    "CountryRemoved",
    "DifferenceCarbonIntensity",
    "SyntheticCarbonIntensity")

#We make convert its numeric columns to the double data type
ResultsPlaceboLOO$Year <- as.numeric(ResultsPlaceboLOO$Year)

ResultsPlaceboLOO$DifferenceCarbonIntensity <-
  as.numeric(ResultsPlaceboLOO$DifferenceCarbonIntensity)

ResultsPlaceboLOO$SyntheticCarbonIntensity <-
  as.numeric(ResultsPlaceboLOO$SyntheticCarbonIntensity)
```



```{r loo placebo plot}
#We plot the differences' path for each possible country's removal
ggplot(data = ResultsPlaceboLOO) + geom_line(aes(x = Year, y = DifferenceCarbonIntensity, color =
                                                   CountryRemoved)) +     scale_color_manual(
                                                     values = c(
                                                       "#D3D3D3",
                                                       "#D3D3D3",
                                                       "#D3D3D3",
                                                       "#D3D3D3",
                                                       "#D3D3D3",
                                                       "#D3D3D3",
                                                       "#D3D3D3",
                                                       "#D3D3D3",
                                                       "#000000",
                                                       "#D3D3D3",
                                                       "#D3D3D3",
                                                       "#D3D3D3",
                                                       "#D3D3D3",
                                                       "#D3D3D3",
                                                       "#D3D3D3"
                                                     )
                                                   ) + geom_line(
                                                     data = subset(ResultsPlaceboLOO, CountryRemoved == "No Country"),
                                                     aes(x = Year, y = DifferenceCarbonIntensity),
                                                     color = "#000000"
                                                   ) + geom_vline(aes(xintercept = 2005), linetype = "dashed") + labs(color = "Removed Country", y =
                                                                                                                                     "CO2e kt per millions of 2015 USD of difference", x="Time")+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))

  
  

```

We try to run the model with only one lagged variable.

```{r Synth with one lagged}
#We prepare the data
SynthDataNoLag <-
  dataprep(
    foo = Data,
    predictors = c(
      "SectorGDPPerCapita",
      "ShareOfSectorGDP",
      "ShareOfLowCarbonEnergy"
    ),
    dependent = "CarbonIntensity",
    unit.variable = "CountryNum",
    unit.names.variable = "Country",
    time.variable = "Year",
    treatment.identifier = 1,
    controls.identifier = c(2:14),
    time.predictors.prior = c(1990:2005),
    time.optimize.ssr = c(1990:2005),
    time.plot = c(1990:2018),
    special.predictors = list(list(8, 1997:2005, "mean"), list(4, 2003 , "mean"))
  )

#We run the Synth process
ResultsNoLag <- synth(SynthDataNoLag)

#We print its results
print(synth.tab(dataprep.res = SynthDataNoLag, synth.res = ResultsNoLag))

#We plot its results
path.plot(
  synth.res = ResultsNoLag,
  dataprep.res = SynthDataNoLag,
  Ylab = "CO2e kt per millions of 2015 USD",
  tr.intake=2005
)


gaps.plot(synth.res = ResultsNoLag,
          dataprep.res = SynthDataNoLag,
          Ylab = "CO2e kt per millions of 2015 USD of difference",
          tr.intake=2005)

```

# Final Results

We compute some metrics to compare Synthetic BC and BC emissions.

```{r metrics calculation}
synthetic_emissions_over_gdp <-
  sum(ResultsPlaceboLOO$SyntheticCarbonIntensity[ResultsPlaceboLOO$Year >
                                                           2005 & ResultsPlaceboLOO$CountryRemoved == "No Country"])

CO2_total_reduction_over_gdp <-
  -sum(ResultsPlaceboLOO$DifferenceCarbonIntensity[ResultsPlaceboLOO$Year > 2005 &
                                          ResultsPlaceboLOO$CountryRemoved == "No Country"])

CO2_average_reduction_over_gdp <-
  -mean(ResultsPlaceboLOO$DifferenceCarbonIntensity[ResultsPlaceboLOO$Year > 2005 &
                                          ResultsPlaceboLOO$CountryRemoved == "No Country"])

CO2_percent_reduction_over_gdp <-
  (CO2_total_reduction_over_gdp / synthetic_emissions_over_gdp) * 100

CO2_last_year_reduction_over_gdp<-    -ResultsPlaceboLOO$DifferenceCarbonIntensity[ResultsPlaceboLOO$Year == 2018 &
                                        ResultsPlaceboLOO$CountryRemoved == "No Country"]

CO2_last_year_percent_reduction_over_gdp <-
  (
    -ResultsPlaceboLOO$DifferenceCarbonIntensity[ResultsPlaceboLOO$Year == 2018 &
                                        ResultsPlaceboLOO$CountryRemoved == "No Country"] / ResultsPlaceboLOO$SyntheticCarbonIntensity[ResultsPlaceboLOO$Year ==
                                                                                                                                                 2018 & ResultsPlaceboLOO$CountryRemoved == "No Country"]
  )*100



#We print these results
print(CO2_total_reduction_over_gdp)
print(CO2_average_reduction_over_gdp)
print(CO2_percent_reduction_over_gdp)
print(CO2_last_year_reduction_over_gdp)
print(CO2_last_year_percent_reduction_over_gdp)

```

Lastly, we clean up our workspace of the variables that won't be needed anymore.

```{r clean-up}
#We remove all of the data we created as that won't be useful anymore
remove(
  BC,
  dataBCCO2,
  dataBCEnergyProduction,
  dataBCPopulation,
  dataBCGDP,
  dataROWGDP,
  dataROWPopulation,
  dataROWEnergyMix,
  dataROWCO2,
  dataUSCPI,
  ROW,
  BCCarbonIntensity,
  BCShareOfLowCarbonEnergy,
  BCSectorGDPPerCapita,
  BCShareOfSectorGDP,
  c,
  i,
  year_quarter,
  dataBCCPI,
  dataBCEnergyProductionPre,
  dataBCGDP2018,
  dataBCGDPPre1997,
  BCCPItemp,
  BCShareOfResearchOverGDP,
  factor,
  GDPtemp,
  POPtemp,
  ROWtemp,
  years,
  controlstemp,
  countries,
  countriesEuro,
  j,
  temp,
  tempres,
  w
)
```

# Additional Code

The following code creates a plot showing BC's Carbon Intensity trajectory compared to that of each of the countries that are part of the control group's set (+ their unweighted average).

```{r no parallel trend plot preparation}
#We create the unweighted average of the control group set's countries
average<-matrix(nrow=0,ncol=8)
for (i in 1:29){
  averagetemp<-"Average of countries"
  averagetemp<-append(averagetemp, 15)
  averagetemp<-append(averagetemp, 1989+i)
  averagetemp<-append(averagetemp,mean(Data$CarbonIntensity[Data$Year==1989+i & Data$CountryNum!=1]))
  averagetemp<-append(averagetemp, mean(Data$SectorGDPPerCapita[Data$Year==1989+i & Data$CountryNum!=1]))
  averagetemp<-append(averagetemp, mean(Data$ShareOfSectorGDP[Data$Year==1989+i & Data$CountryNum!=1]))
  averagetemp<-append(averagetemp, mean(Data$ShareOfLowCarbonEnergy[Data$Year==1989+i & Data$CountryNum!=1]))
  averagetemp<-append(averagetemp, mean(Data$ShareOfResearchOverGDP[Data$Year==1989+i & Data$CountryNum!=1]))
  average<-rbind(average,averagetemp)
}

#We turn it into a dataframe
average = as.data.frame(average)

#We rename its columns to match our previous dataset
dimnames(average)[[2]] <-
  c(
    "Country",
    "CountryNum",
    "Year",
    "CarbonIntensity",
    "SectorGDPPerCapita",
    "ShareOfSectorGDP",
    "ShareOfLowCarbonEnergy",
    "ShareOfResearchOverGDP"
  )

#We combine the unweighted average with the rest of the data
Dataaverage <- rbind(Data, average)

#We convert all the numbers in it in doubles
Dataaverage[, 2:8] <-
  lapply(Dataaverage[, 2:8], function(x)
    if (is.character(x))
      as.numeric(x)
    else
      x)
```



```{r no parallel trend plot}
for (i in 2:15){
  
print(ggplot(data = Dataaverage[Dataaverage$CountryNum==i | Dataaverage$CountryNum==1,]) + geom_line(aes(x = Year, y = CarbonIntensity, color =
                                      Country)))
  }

```

